The Multi-Stencil Language

### 2016-01-29 ARTICLES/IJPP/article/article.tex
article IJPP Helene 26/01/2016

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfig}
\usepackage{caption}
\usepackage{cite}
\usepackage{filecontents}
\usepackage{listings}
\usepackage{tikz}
\usepackage[ruled,noend]{algorithm2e}
\usetikzlibrary{calc,arrows,shapes,automata,petri,positioning,decorations.markings,shadows}

@@

\institute{Helene Coullon \and Christian Perez \at
              INRIA \\
              46 Allée d'Italie\\
              69007 Lyon\\
              \email{helene.coullon@inria.fr}
           \and
           Julien Bigot \at
              CEA
}

@@

%------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}
Contributions :
\begin{itemize}
\item Formalism of a multi-stencil program and its parallelization
\item The Multi-stencil Language: agnostic from the type of mesh and of the choosen implementation
\item A first implementation of the MSL compiler (static scheduling + fusion + dump to SkelGIS/components)
\item Evaluation of the different types of parallelism introduced + compiler + fusion
\end{itemize}
%------------------------------------------------------------------------------
\section{Computational model of Multi-Stencil Programs}
\label{sect:formalism}
\input{formalism.tex}
% Formalism :
% \begin{itemize}
% \item mesh / mesh entities and groups / computations domains
% \item data and scalars
% \item computations : stencil, local and reduction
% \item Multi-Stencil Program
% \end{itemize}
%------------------------------------------------------------------------------
\section{Parallelization of Multi-Stencil Programs}
\label{sect:parallelism}
\input{parallelism.tex}
% Parallelization formalism :
% \begin{itemize}
% \item Data parallelism (introduction of synchronizations)
% \item Task parallelism (computation of the dependency graph)
% \end{itemize}
%------------------------------------------------------------------------------
\section{The Multi-Stencil Language}
\label{sect:msl}
\input{msl.tex}
% The parallel empty skeleton of the application can be computed automatically from the language :
% \begin{itemize}
% \item grammar
% \item example from the language to the dependency graph
% \end{itemize}
%------------------------------------------------------------------------------
\section{Static Scheduling}
\label{sect:msp}
\input{msp.tex}
% From the dependency graph we study a first dump: static scheduling
% \begin{itemize}
% \item description of the algorithm to get the binary tree decomposition of a minimal serie-parallel graph
% \item use of the serie-parallel tree decomposition to detect fusions of kernels
% \item example (the same one) from the dependency graph to the binary tree
% \end{itemize}
%------------------------------------------------------------------------------
\section{Evaluation}
\label{sect:eval}
\begin{itemize}
\item short description of the implementation (compiler in Python, DDS = SkelGIS, Components)
\item evaluation of the compiler (execution times of the different steps)
\item evaluation of the data parallelism (weak/strong scaling)

@@

\bibliographystyle{spbasic}
\bibliography{biblio}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfig}
\usepackage{caption}
\usepackage{cite}
\usepackage{filecontents}
\usepackage{listings}
\usepackage{mathtools, cuted}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usetikzlibrary{calc,arrows,shapes,automata,petri,positioning,decorations.markings,shadows}

@@

\institute{Helene Coullon \and Christian Perez \at
              INRIA \\
              46 Allée d'Italie\\
              69007 Lyon\\
              \email{helene.coullon@inria.fr}
           \and
           Julien Bigot \at
           Maison de la Simulation, CEA, CNRS, Univ. Paris-Sud, UVSQ, Universit\'e Paris-Saclay, 91191 Gif-sur-Yvette, France\\
           \email{julien.bigot@cea.fr}
}

@@

%------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}
Contributions :
\begin{itemize}
\item Formalism of a multi-stencil program and its parallelization
\item The Multi-stencil Language: agnostic from the type of mesh and of the choosen implementation
\item A first implementation of the MSL compiler (static scheduling + fusion + dump to SkelGIS/components)
\item Evaluation of the different types of parallelism introduced + compiler + fusion
\end{itemize}
%------------------------------------------------------------------------------
\section{Computational model of Multi-Stencil Programs}
\label{sect:formalism}
\input{formalism.tex}
% Formalism :
% \begin{itemize}
% \item mesh / mesh entities and groups / computations domains
% \item data and scalars
% \item computations : stencil, local and reduction
% \item Multi-Stencil Program
% \end{itemize}
%------------------------------------------------------------------------------
\section{Parallelization of Multi-Stencil Programs}
\label{sect:parallelism}
\input{parallelism.tex}
% Parallelization formalism :
% \begin{itemize}
% \item Data parallelism (introduction of synchronizations)
% \item Task parallelism (computation of the dependency graph)
% \end{itemize}
%------------------------------------------------------------------------------
\section{The Multi-Stencil Language}
\label{sect:msl}
\input{msl.tex}
The parallel empty skeleton of the application can be computed automatically from the language :
\begin{itemize}
\item grammar
\item example from the language to $\Gamma$
\end{itemize}
%------------------------------------------------------------------------------
\section{Static Scheduling}
\label{sect:msp}
\input{msp.tex}
% From the dependency graph we study a first dump: static scheduling
% \begin{itemize}
% \item description of the algorithm to get the binary tree decomposition of a minimal serie-parallel graph
% \item use of the serie-parallel tree decomposition to detect fusions of kernels
% \item example (the same one) from the dependency graph to the binary tree
% \end{itemize}
%------------------------------------------------------------------------------
\section{MSL Compiler}
\label{sect:comp}
\input{compiler.tex}
\begin{itemize}
\item Overall algrotihm~\ref{alg:compiler}
\item Big example from the language to the static sheduling/optimization~\ref{fig:example}
\end{itemize}
%------------------------------------------------------------------------------
\section{Evaluation}
\label{sect:eval}
\begin{itemize}
\item short description of the implementation (compiler in Python, DDS = SkelGIS, Components)
\item evaluation of the compiler (execution times of the different steps)
\item evaluation of the data parallelism (weak/strong scaling)

@@

\bibliographystyle{plain}
\bibliography{biblio}
